---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# widgetdown

[![Travis build status](https://travis-ci.org/jayhesselberth/widgetdown.svg?branch=master)](https://travis-ci.org/jayhesselberth/widgetdown)

The goal of widgetdown is to test the use of htmlwidgets in a pkgdown website, without bloating the [pkgdown](https://github.com/r-lib/pkgdown) package itself.

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jayhesselberth/widgetdown")
```
## README widgets

```{r, echo=FALSE}
# set seed for reproducible widget id
if (requireNamespace("htmltools", quietly = TRUE)) {
  htmlwidgets::setWidgetIdSeed(42)
}
```

The package tests the use of htmlwidgets in pkgdown:

* [Home page](https://jayhesselberth.github.io/widgetdown/index.html) (i.e., `README.Rmd` or `index.Rmd`)
* [Reference topics](https://jayhesselberth.github.io/widgetdown/reference/test-widgets.html) using Rd `@examples`.
* [Vignettes](https://jayhesselberth.github.io/widgetdown/articles/widget.html)

widgetdown tests the following widgets:

* [`leaflet`](https://github.com/rstudio/leaflet/)
* [`d3heatmap`](https://github.com/rstudio/d3heatmap)
* [`DT`](https://github.com/rstudio/DT)
* [`plotly`](https://plot.ly/r/)

### leaflet

```{r leaflet}
library(leaflet)
  leaflet() %>%
  addTiles() %>%
  addMarkers(
  lng=174.768,
  lat=-36.852,
  popup="The birthplace of R"
)
```

### d3heatmap

```{r d3}
library(d3heatmap)
d3heatmap(mtcars, scale = "column", colors = "Blues")
```

### DT
```{r dt}
library(DT)
datatable(iris)
```

### plotly

```{r plotly}
library(plotly)
plot_ly(midwest,
  x = ~percollege,
  color = ~state,
  type = "box"
)
```

